%% ============================================================
%%  Academic Curriculum Vitae — Mengnan (Monica) Xu
%%  Target: Postdoctoral Fellow, CCCW, University of Hong Kong
%%  Compiled with pdflatex
%%
%%  INSTRUCTIONS FOR CANDIDATE:
%%  1. Fill in actual publication titles/venues in the
%%     "Working Papers & Publications" section.
%%  2. Add/remove conference presentations as appropriate.
%%  3. Add dissertation committee members' names.
%%  4. Run:  pdflatex cv_academic.tex  (twice for page refs)
%% ============================================================

\documentclass[11pt, letterpaper]{article}

%% ---- Packages -----------------------------------------------
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{mathptmx}          % Times New Roman — standard in social science
\usepackage[margin=1in, top=0.85in, bottom=0.85in]{geometry}
\usepackage{microtype}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{url}

%% ---- Page style ---------------------------------------------
\pagestyle{fancy}
\fancyhf{}
\fancyhead[R]{\small\itshape Xu --- \thepage\ of \pageref{LastPage}}
\renewcommand{\headrulewidth}{0pt}

%% ---- Section formatting ------------------------------------
\titleformat{\section}
  {\large\bfseries\scshape}
  {}
  {0em}
  {}
  [\vspace{-6pt}\rule{\linewidth}{0.6pt}]
\titlespacing*{\section}{0pt}{14pt}{6pt}

%% ---- Entry commands -----------------------------------------

% Two-column education / experience header
\newcommand{\cventry}[4]{%
  % #1 = year(s), #2 = title/degree, #3 = institution, #4 = location
  \noindent\textbf{#2}\\
  \textit{#3}, #4 \hfill \textit{#1}\par\vspace{3pt}
}

% Hanging-indent bibliography entry
\newcommand{\pubentry}[1]{%
  \noindent\hangindent=1.2em\hangafter=1 #1\par\vspace{4pt}
}

%% ---- List settings -----------------------------------------
\setlist[itemize]{
  leftmargin=1.5em,
  itemsep=1pt,
  topsep=3pt,
  parsep=0pt
}

\setlength{\parskip}{5pt}
\setlength{\parindent}{0pt}

%% ============================================================
\begin{document}

%% ---- Header ------------------------------------------------
\begin{center}
  {\LARGE\bfseries Mengnan Xu}\\[6pt]
  \small
  (512)\,808-6808\quad
  \href{mailto:mnchu007@hotmail.com}{mnchu007@hotmail.com}\\[2pt]
  \textit{PhD in Public Management (defense May 2026),
          Beijing Normal University}
\end{center}

\vspace{4pt}

%% ---- Research Interests ------------------------------------
\section{Research Interests}

Chinese politics and governance; state capacity and organizational mobilization;
development governance; China's poverty alleviation programs; AI and
computational methods for social science; political economy of China;
South--South cooperation and international development.

%% ---- Education ---------------------------------------------
\section{Education}

\noindent
\begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
  \textbf{Ph.D., Public Management}
    & \textit{Oct 2018 -- May 2026}\\
  \textit{Beijing Normal University, School of Social Development and Public Policy}
    & Beijing, China\\[4pt]
  \textbf{Master of Public Management}
    & \textit{Sep 2016 -- Jun 2018}\\
  \textit{Beijing Normal University, School of Social Development and Public Policy}
    & Beijing, China\\[4pt]
  \textbf{Master of Science, Information Technology and Management}
    & \textit{Jul 2023 -- May 2024}\\
  \textit{University of Texas at Austin, McCombs School of Business}
    & Austin, TX, USA\\
  \multicolumn{2}{@{}l@{}}{\small\textit{Concurrent with doctoral study at Beijing Normal University.}}\\[4pt]
  \textbf{Bachelor of Management Science \& Engineering (MIS)}
    & \textit{Sep 2008 -- Jun 2012}\\
  \textit{Central South University}
    & Changsha, China\\
\end{tabular*}

\vspace{6pt}
\noindent\textbf{Doctoral Dissertation:}\\
\textit{The Impact of Targeted Poverty Alleviation Policies on Long-Term Development and Vulnerability to Poverty Relapse Among Rural Households: Evidence from a Quasi-Natural Experiment Using CFPS Panel Data}\\
Beijing Normal University, School of Social Development and Public Policy.\\
\small\textit{Passed blind external review; oral defense scheduled May 2026.}

%% ---- Visiting Positions ------------------------------------
\section{Visiting Positions}

\noindent
\begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
  \textbf{Visiting Doctoral Researcher}
    & \textit{Aug 2021 -- Aug 2022}\\
  \textit{Department of Government, University of Texas at Austin}
    & Austin, TX, USA\\
  \multicolumn{2}{@{}l@{}}{\small\textit{China Scholarship Council Fellowship}}\\[4pt]
  \textbf{Visiting Scholar}
    & \textit{Sep -- Oct 2019}\\
  \textit{University of Oxford}
    & Oxford, UK\\
\end{tabular*}

%% ---- Fellowships & Awards ----------------------------------
\section{Fellowships and Awards}

\pubentry{China Scholarship Council (CSC) Fellowship for Visiting Doctoral Research,
Department of Government, University of Texas at Austin. Aug 2021--Aug 2022.}

\pubentry{STEPS Summer School Scholarship, Institute of Development Studies (IDS),
University of Sussex. 2021.}

\pubentry{Young Scholars Forum Scholarship, University of Hong Kong. Jul 2019.}

%% ---- Working Papers & Publications -------------------------
\section{Publications \& Working Papers}

\pubentry{\textbf{Xu, Mengnan}, Robert Walker, and Lichao Yang.
``Poor and Lazy: Understanding Middle-Class Perceptions of Poverty in China.''
\textit{Journal of Contemporary China}, 31(136), 756--769, 2022.
DOI: 10.1080/10670564.2021.2010878. (SSCI Q1; \textbf{First Author})}

\pubentry{Xiaoxin Xu, Xiulan Zhang, Teh Wei Hu, Leonard S Miller, \textbf{Xu, Mengnan} et al.
``Tobacco Control Policy Evaluation in China: Evidence from Administrative Panel Data.''
\textit{BMJ Open}, 2019.}

\pubentry{Xiulan Zhang, Xiaoxin Xu, \textbf{Xu, Mengnan}, and Teh-wei Hu.
``The Impact of Tobacco Taxation Policy on Slim Cigarette Use and the Growing Popularity of Slim Cigarettes in China Since 2014.''
\textit{Health}, 2019.}

\pubentry{Xiulan Zhang, \textbf{Xu, Mengnan.} ``Organizational Ecology and Multi-Actor
State Mobilization in China's Poverty Alleviation Governance.''
\textit{Working paper. Original database complete; manuscript under revision;
submission planned during postdoctoral fellowship.}}

\pubentry{Xiulan Zhang, \textbf{Xu, Mengnan.} ``Computational Methods for Large-Scale
Chinese Policy Document Analysis: A Text-as-Data Approach to Governance
Research.'' \textit{Working paper. Data collection and processing complete;
writing in progress; submission planned during postdoctoral fellowship.}}

%% ---- Research Experience -----------------------------------
\section{Research Experience}

\noindent\textbf{Technical Research Analyst}
\hfill \textit{Sep 2016 -- May 2018}\\
\textit{Gates Foundation–Funded Research Initiative,
Beijing Normal University} \hfill Beijing, China

\begin{itemize}
  \item Led end-to-end coordination of multi-year research programs on
        development governance and public administration reform, aligning
        international funding requirements with academic deliverables.
  \item Designed and executed large-scale quantitative and qualitative data
        collection; performed statistical analysis using SAS, Stata, and Python to
        support policy recommendations.
  \item Built an original organizational ecology database tracking actors,
        resource flows, and governance logic across China's national non-profit organization, drawing on yearbooks,
        government reports, and policy documents.
  \item Applied data ETL pipelines (topic modeling, named-entity recognition,
        keyword co-occurrence networks) to Chinese-language policy corpora
        exceeding 10,000 documents.
  \item Translated empirical findings into policy briefs and analytical
        reports for program leadership and external stakeholders.
  \item Managed annual planning, milestone tracking, and cross-institutional
        coordination across government, university, and foundation partners.
\end{itemize}

\vspace{6pt}
\noindent\textbf{Graduate Research Assistant, Public Management}
\hfill \textit{Sep 2016 -- Jun 2018}\\
\textit{Beijing Normal University, School of Government}
\hfill Beijing, China

\begin{itemize}
  \item Conducted literature reviews, archival research, and comparative policy
        analysis on Chinese governance, state-society relations, and public
        administration.
  \item Contributed to faculty research projects examining central--local
        government relations and organizational reform in China.
\end{itemize}

%% ---- Teaching Experience -----------------------------------
% \section{Teaching Experience}
% Add any teaching assistantships or courses taught here.

%\noindent\textit{[Teaching assistant roles or courses taught at Beijing Normal University may be listed here.]}

%% ---- Conference Presentations ------------------------------
\section{Conference Presentations}

\pubentry{``The Concern of Netizens towards Electronic Cigarette in Their
Internet Search Behavior.''
China--Korea Academic Exchange Forum (Beijing Normal University \& Soongsil University),
Beijing, China. October 2019.
\textit{First Prize; Best Presentation Award.}}

\pubentry{``The Concern of Netizens towards Electronic Cigarette in
Their Internet Search Behavior.''
Annual Research Postgraduate Conference, University of Hong Kong,
Hong Kong. June 2019.}

\pubentry{``Consensus Guidance, Policy Advocacy Mechanism on China Tobacco Control.''
China--Korea Academic Exchange Forum (Beijing Normal University \& Soongsil University),
Seoul, South Korea. May 2018.}

%% ---- Relevant Professional Experience ----------------------
\section{Relevant Professional Experience}

\noindent\textbf{Software Engineer / AI Engineer}
\hfill \textit{Jun 2025 -- Mar 2026}\\
\textit{Apple Inc.} \hfill Austin, TX, USA
\begin{itemize}
  \item Developed components for Apple's Intelligence platform, focusing on
        production-scale natural language processing pipelines and
        retrieval-augmented generation architectures.
  \item Applied large language model techniques to large-scale information
        processing and knowledge integration systems, gaining first-hand
        engineering experience with the tools now central to computational
        social science.
\end{itemize}

\vspace{6pt}
\noindent\textbf{Software Engineer}
\hfill \textit{Apr 2026 -- Present}\\
\textit{Applied Optical Technologies} \hfill Houston, TX, USA
\begin{itemize}
  \item Built full-pipeline automated data monitoring and analytics system
        for manufacturing execution processes.
  \item Designed modules for large-scale data collection, cleaning, and
        multi-dimensional statistical analysis.
\end{itemize}

\vspace{6pt}
\noindent\textbf{Senior Risk Analyst}
\hfill \textit{Jul 2012 -- Jun 2016}\\
\textit{Agricultural Bank of China} \hfill Hengyang, China
\begin{itemize}
  \item Extracted and analyzed large-scale financial datasets using SQL and
        statistical modeling to support risk management and policy analytics.
  \item Developed credit scoring models (logistic regression, WOE binning)
        that reduced default rates and improved loan processing efficiency.
\end{itemize}

%% ---- Methodological & Technical Skills ---------------------
\section{Methodological and Technical Skills}

\noindent\textbf{Quantitative and Computational Methods:}
Regression analysis, difference-in-differences, network analysis,
causal inference; Python (pandas, NumPy, scikit-learn), R, SQL, STATA/SAS.

\noindent\textbf{AI and NLP for Social Science:}
Large language models (fine-tuning, retrieval-augmented generation,
prompt engineering), topic modeling (LDA, BERTopic), named-entity recognition,
text classification, word embeddings; LangChain, OpenAI API, Hugging Face, AI agentic engineering.

\noindent\textbf{Data Infrastructure:}
AWS (S3, Lambda, SageMaker), BigQuery, MySQL, MongoDB; Git, Jupyter,
Tableau, Power BI.

\noindent\textbf{Research Methods:}
Archival and documentary analysis, qualitative case study, elite
interviews, survey research.

%% ---- Languages ---------------------------------------------
\section{Languages}

\begin{tabular}{@{}ll}
  Mandarin Chinese & Native \\
  English          & Proficient (academic writing, presentations, and publication) \\
\end{tabular}

%% ---- References --------------------------------------------
\section{References}

Available upon request.

\end{document}
